The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-01-28 paper/sections/methods.tex
took a pass on otman's comments

%%single projector for every object
When assembled for all parts,~\refeq{hfit}, yields a block upper triangular matrix $U$ and a sparse matrix $B$ ~(\reffig{multiparts}) which can be used to efficiently to compute the projection 
operator for the entire object $\Pi = U^{-1}B$. 
The structure of $U$ and $B$ ensures that $\Pi$ only couples objects which share deformation centers, which implies a sparse $\Pi$. 
The per-part projection operators $\Pi_i$ correspond to blocks of rows of $\Pi$. 
Coupling via the deformation origins ensures our method will reproduce rigid and linear deformations in regions around these points, while higher order 
terms help compensate for more local deformations.

@@

\begin{equation}
    \defX\left(\refX\right) = \underbrace{\shapef\left(\refX\right)\bldmat\Pi}_{\Jkin\left(\refX\right)}\vc{q},
\end{equation} where $\shapef\in\real^{3\times n} = \begin{bmatrix}P_1\left(\refX\right) \dots P_m\left(\refX\right)\end{bmatrix}$, $m$ is number of 
parts in the object, $\bldmat$ is the diagonal matrix of blending weights, $\Pi$ is the global projection operator and $\Jkin\left(\refX\right)$ is the kinematic Jacobian.

>>>>

%%single projector for every object
When assembled for all parts,~\refeq{hfit}, yields a block upper triangular matrix $U$ and a sparse matrix $B$ ~(\reffig{multiparts}) which can be used to efficiently compute the projection 
operator for the entire object $\Pi = U^{-1}B$. 
The structure of $U$ and $B$ ensures that $\Pi$ only couples objects which share deformation centers, which implies a sparse $\Pi$. 
The per-part projection operators $\Pi_i$ correspond to blocks of rows of $\Pi$. 
Coupling via the deformation origins ensures our method will reproduce rigid and linear deformations in regions around these points, while higher order 
terms help compensate for more local deformations.

@@

\begin{equation}
    \defX\left(\refX\right) = \underbrace{\shapef\left(\refX\right)\bldmat\Pi}_{\Jkin\left(\refX\right)}\vc{q},
\end{equation} where $\shapef\in\real^{3\times n} = \begin{bmatrix}P_1\left(\refX\right) \dots P_m\left(\refX\right)\end{bmatrix}$, $m$ is the number of 
parts in the object, $\bldmat$ is the diagonal matrix of blending weights, $\Pi$ is the global projection operator and $\Jkin\left(\refX\right)$ is the kinematic Jacobian.
